Title

### 2018-08-31 thesis/paper/paper.tex
Improved one-of qualifier value

\subsection{One-of qualifier value (Q52712340)}
The one-of qualifier value constraint restricts which values may be used on a qualifier with a given property on a constrained statement.

\begin{table}[H]
\caption{One-of qualifier value constraint (Q52712340)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & constrained statement qualifier value \\
\hline
Qualifiers: & \makecell{qualifier property (P2306) -- 1 \\ property of the restricted qualifier\\
qualifier values (P2305) -- 1..* \\ values the qualifiers may take}\\
\hline
Violation & \makecell{constrained statement with a qualifier with the qualifier property and a value unequal to all qualifier values} \\
\hline
Dependency & constrained item and qualifiers with the qualifier property \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

The constraint can be modelled if the inequality between a value of a qualifier property with all qualifier values is given. The violations could then be found by taking a statementEDB with the constrained property and a qualifier with the qualifier property on the former statement whose value is unequal to all qualifier values.

@@

\subsection{One-of qualifier value (Q52712340)}
The one-of qualifier value constraint is violated if a constrained statement has a qualifier with a value unequal to all allowed values. Inequality needs to be pre-processed between all values of qualifiers on constrained statements. With the set of allowed Values \(A\) the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{qualifierEDB}(S, \text{qualifierProperty}, O) \wedge \text{unequal}(\{A\}, O)
\end{split}
\end{equation*}

>>>>

\subsection{One-of qualifier value (Q52712340)}
\subsubsection{Constraint}
The \emph{one-of qualifier value} constraint restricts which \emph{qualifier values} may be used on a qualifier with a given \emph{qualifier property} on a constrained statement.

\begin{table}[H]
\caption{One-of qualifier value constraint (Q52712340)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & constrained statements and their qualifiers \\
\hline
Qualifiers: & \makecell{\emph{qualifier property} (P2306) -- 1 \\ property that, if used as predicate, constrains a qualifier \\
\emph{qualifier values} (P2305) -- 1..* \\ values that are allowed for qualifiers on constrained statements \\ with the \emph{qualifier property} as predicate}\\
\hline
Violation & \makecell{constrained statement with a qualifier with the qualifier property \\ and a value unequal to all qualifier values} \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

\subsubsection{Rules}
The one-of qualifier value constraint is violated if a constrained statement has a qualifier with a value unequal to all allowed values. Inequality needs to be established between all values of qualifiers and all allowed values. With the set of allowed Values \(A\) the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{qualifierEDB}(S, \text{qualifierProperty}, O) \wedge \text{unequal}(\{A\}, O)
\end{split}
\end{equation*}

@@
